---
title: "p8105_hw1_cj2793"
author: "Chenyu Jin"
date: "2024-09-12"
output: github_document
---

# Problem 1

Firstly, we input the dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

Then, we give a short description of the penguins dataset:

1. We should know the data in this dataset:
```{r}
View(penguins)
summary(penguins)
```
According to the View() and summary() results, we have 8 variables in our dataset. From these variables, we know that there are 3 species of penguins in our dataset and they live in 3 different island. This dataset includes the bill length, bill depth, flipper length and body mass of each penguin. There are 165 female penguins and 168 male penguins. Unfortunately, 11 of them are unknown of sex. The data were collected during 2007 to 2009.

2. We should know the data size in this dataset:
```{r}
nrow(penguins)
ncol(penguins)
```
According to the results, we know that we have 344 rows (observations) and 8 column
(variables) in our dataset.

3. We should know the mean flipper length of the penguins in the dataset:
```{r}
library(tidyverse)
flipper_length <-- pull(penguins, flipper_length_mm)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
Because there is missing data in the dataset, we should use na.rm argument in
mean() function. According to the result, we know that the mean flipper length 
of the penguins is 200.9152mm.

Next, we should make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x)
and then save it.
```{r}
library(ggplot2)

ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point() + labs(title = "Scatterplot of Flipper Length vs Bill Length",
                    x = "Bill Length (mm)",
                    y = "Flipper Length (mm)")

ggsave("scatterplot flipper vs bill length.png")
```
# Problem 2

Firstly, we create a data frame:
```{r}
library(tidyverse)
set.seed(1)

normal_sample <- rnorm(10)
logical_vector <- normal_sample > 0
char_vector <- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J")
factor_vector <- factor(sample(c("L0", "L1", "L2"), 10, replace = TRUE))

df <- tibble(
  Normal_Sample = normal_sample,
  Logical_Vector = logical_vector,
  Char_Vector = char_vector,
  Factor_Vector = factor_vector
)
```

Then, we try to take the mean of each variable in your data frame:
```{r}
mean(pull(df, Normal_Sample))
mean(pull(df, Logical_Vector))
mean(pull(df, Char_Vector))
mean(pull(df, Factor_Vector))
```
We can see that:
For Normal Sample: Mean can be calculated as 0.1322028;
For Logical Vector: Mean can be calculated as 0.6;
For character Vector: Mean cannot be calculated;
For Factor Vector: Mean cannot be calculated.

Finally, we try to convert variables from one type to another:
```{r eval=FALSE}
logical_numeric <- as.numeric(pull(df, Logical_Vector))
char_numeric <- as.numeric(pull(df, Char_Vector))
factor_numeric <- as.numeric(pull(df, Factor_Vector))
```
Here, we can see that:

When we convert a logical vector to numeric, TRUE becomes 1 and FALSE becomes 0;
When we take the mean of a logical vector, it's treated as a numeric vector with 0 and 1.
As a result, it works.

When we convert a character vector to numeric, it will produce NA because characters cannot be meaningfully coerced into numeric values;
As a result, when we try to calculate the mean of character vector, it does not work.

When we convert a factor vector to numeric each level of the factor is represented by an integer (L0 = 1; L1 = 2; L2 = 3);
When we calculate the mean of a factor vector, it is calculating the integer which is not
actually the levels; As a result, it does not work.

